---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

__Note__: This R package is not mean to be "serious". It's just for homework. 

# `WZZ`

This is an R package that gives `sqrt()` friends by providing other power functions. 
It also helps do BoxCox transformation/ BoxCox inverse transformation.

## Installation

You can install powers from github with:
```{r}
# install.packages("devtools")
devtools::install_github("wenzhengzzz/STAT547-hw09-Zhou-Wenzheng")
```

## Functions

- suqare(x, plot.it=FALSE) is used to take suqare of a vector x, it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values.

- cube(x, plot.it=FALSE) is used to cube a vector x,  it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values.

- BoxCox(x,lambda,plot.it=F,omit.na=T) is used to do BoxCox transformation of a vector x, it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values and omit NA in the data.

- BoxCox.inv(x,lambda,plot.it=F,omit.na=T) is used to do inverse BoxCox transformation of a vector x, 
it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values and omit NA in the data.

## Example

See the vignette for more extensive use, but here's some examples:

```{r example}
WZZ::square(2,F)
WZZ::cube(c(2,3))
WZZ::BoxCox(2,1,T)
WZZ::BoxCox.inv(2,1)
```

## For Developers

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)

Use the internal `pow` function as the machinery for the front-end functions such as `square`and `cube`. 
