---
title: "Using the `WZZ` package"
author: "Wenzheng Zhou"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(WZZ)
```

## Functions

- suqare(x, plot.it=FALSE) is used to take suqare of a vector x, it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values.

- cube(x, plot.it=FALSE) is used to cube a vector x,  it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values.

- BoxCox(x,lambda,plot.it=F,omit.na=T) is used to do BoxCox transformation of a vector x, it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values and omit NA in the data.

- BoxCox.inv(x,lambda,plot.it=F,omit.na=T) is used to do inverse BoxCox transformation of a vector x, 
it can be logicals and nuumbers. 
There is an option to plot the vector vs returned values and omit NA in the data.

## Usage

### Want squares, cubes, or Box-Cox transformation? Easy.

```{r}
square(1:10)
cube(1:10)
BoxCox(1:10,1)
BoxCox.inv(1:10,1)
```

### The function is plot friendly !

```{r}
square(1:10,plot.it = T)
```

```{r}
BoxCox.inv(1:10,2,plot.it = T)
```

### Could omit NA from vectors in BoxCox/inverse transformation

```{r}
BoxCox(c(1,NA,2),2,plot.it = F,omit.na = F)
BoxCox(c(1,NA,2),2,plot.it = F)
```

### All functions can be operated on logicals or even mixed vectors!

```{r}
logic_vec <- c(TRUE, TRUE, FALSE)
square(logic_vec)
cube(logic_vec)
BoxCox(logic_vec,1)
BoxCox.inv(logic_vec,1)
```
```{r}
a <- c(TRUE,1,2)
cube(a)
BoxCox(a,1)
```

## Advanced Use

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7) 
## So base-R-boring!
lapply(my_list, function(x) x^2) 
## Use powers instead!
lapply(my_list, square)
```

```{r}
lapply(my_list, BoxCox,lambda=1)
```

## Errors

1. All functions in this package are not allowed strings in operating vectors. 

```{r error=TRUE}
square("a")
cube(c("1",1))
```
```{r error=TRUE}
BoxCox("a",1)
BoxCox.inv(c("a",2,1),1)
```

2. BoxCox and BoxCox.inv also require positive values of vector for certain lambda. It is built in the process of calculating BoxCox transformation.

```{r error=TRUE}
BoxCox(-1,1/2)
BoxCox.inv(-1,3/2)
```

